EagerNet: Early Predictions of Neural Networks for Computationally Efficient Intrusion Detection

### 2020-07-21 paper/paper.tex

>>>>

\begin{figure*}
\center
\begin{tabular}{cccc}
\subfloat[CIC-IDS17 (3 layers $\times$ 128 neurons).]{\includegraphics[width = 2.5in]{figures/conf-acc-17-3x128.pdf}} &
\subfloat[CIC-IDS17 (12 layers $\times$ 64 neurons).]{\includegraphics[width = 2.5in]{figures/conf-acc-17-12x64.pdf}}\\
\subfloat[UNSW-NB15 (3 layers $\times$ 128 neurons).]{\includegraphics[width = 2.5in]{figures/conf-acc-15-3x128.pdf}} &
\subfloat[UNSW-NB15 (12 layers $\times$ 64 neurons).]{\includegraphics[width = 2.5in]{figures/conf-acc-15-12x64.pdf}}
\end{tabular}
\caption{Confidence threshold effect on accuracy and number of needed layers.}
\label{fig:confidence}
\end{figure*}

\begin{figure}
\center
\begin{tabular}{cccc}
\subfloat[CIC-IDS17 (12 layers $\times$ 64 neurons).]{\includegraphics[width = 0.85\columnwidth]{figures/multiclass17.pdf}} \\
\subfloat[UNSW-NB15 (12 layers $\times$ 64 neurons).]{\includegraphics[width = \columnwidth]{figures/multiclass15.pdf}}
\end{tabular}
\caption{Accuracy plot multiclass.}
\end{figure}
